*Symbiodinium* communities in reef corals of St. John, U.S.V.I. (2012)

### 2016-09-07 analysis/STJ2012_analysis.Rmd
small formatting changes

# *Symbiodinium* in each coral
For each coral species, barplots are presented showing the relative abundance of OTUs obtained by 100%, 97%, and 97%-within-sample clustering. OTUs comprising more than 4% of a sample are labeled with the unique OTU number and the *Symbiodinium* subtype and NCBI GenBank accession number of the closest BLAST hit for that OTU in the reference database. OTU numbers and barplot colors are NOT comparable across the three clustering methods.

## *Diploria strigosa*  
Notice how 97% OTUs and 97% within-sample OTUs are **NOT THE SAME!** Specifically, notice how in the 97% OTU dataset, all samples except two are dominated by the same OTU, denovo235. In the 97% within-sample OTU dataset, those samples are dominated by three different OTUs -- denovo73, denovo231, and denovo10. Look at the 100% OTU dataset to see the composition of unique sequence variants in these samples. Indeed, these samples are dominated by **different sequence variants**. However, in the 97% OTU approach, they have all been collapsed into the same OTU, while in the 97% within-sample clustering approach, samples with different dominant sequence variants are maintained as separate OTUs, even though these different sequence variants are more than 97% similar to each other. I suggest that the  within-sample clustering approach is a better way of treating *Symbiodinium* ITS2 sequence data.
```{r dstr, cache=T, fig.height=16, fig.width=8}
# Create subsetted phyloseq objects for Diploria strigosa
dstr97.f.p <- subset_samples(phy97.f.p, Species=="strigosa")
dstr97bs.f.p <- subset_samples(phy97bs.f.p, Species=="strigosa")
dstr97bsp.f.p <- subset_samples(phy97bsp.f.p, Species=="strigosa")
dstr100.f.p <- subset_samples(phy100.f.p, Species=="strigosa")
# Plot custom barplots for Diploria strigosa
par(mfrow=c(4,1), mar=c(4,4,2,0), mgp=c(0,0.5,0), lwd=0.1)
otubarplot(dstr97.f.p, main="97% OTUs")
otubarplot(dstr97bsp.f.p, main="97% within-species OTUs")
otubarplot(dstr97bs.f.p, main="97% within-sample OTUs")
otubarplot(dstr100.f.p, main="100% OTUs")
```

>>>>

# *Symbiodinium* in each coral
For each coral species, barplots are presented showing the relative abundance of OTUs obtained by 100%, 97%, and 97%-within-sample clustering. OTUs comprising more than 4% of a sample are labeled with the unique OTU number and the *Symbiodinium* subtype and NCBI GenBank accession number of the closest BLAST hit for that OTU in the reference database. OTU numbers and barplot colors are NOT comparable across clustering methods.

## *Diploria strigosa*  
Notice how 97% OTUs and 97% within-sample OTUs are **NOT THE SAME!** Specifically, notice how in the 97% OTU dataset, all samples except two are dominated by the same OTU, B1. In the 97% within-sample OTU dataset, those samples are dominated by three different OTUs -- B1, [B1]^6, and [B1]^3. Look at the 100% OTU dataset to see the composition of unique sequence variants in these samples. Indeed, these samples are dominated by **different sequence variants**. However, in the 97% OTU approach, they have all been collapsed into the same OTU, while in the 97% within-sample clustering approach, samples with different dominant sequence variants are maintained as separate OTUs, even though these different sequence variants are more than 97% similar to each other. I suggest that the  within-sample clustering approach is a better way of treating *Symbiodinium* ITS2 sequence data.
```{r dstr, cache=T, fig.height=16, fig.width=8}
# Create subsetted phyloseq objects for Diploria strigosa
dstr97.f.p <- subset_samples(phy97.f.p, Species=="strigosa")
dstr97bs.f.p <- subset_samples(phy97bs.f.p, Species=="strigosa")
dstr97bsp.f.p <- subset_samples(phy97bsp.f.p, Species=="strigosa")
dstr100.f.p <- subset_samples(phy100.f.p, Species=="strigosa")
# Plot custom barplots for Diploria strigosa
par(mfrow=c(4,1), mar=c(4,4,2,0), mgp=c(0,0.5,0), lwd=0.1)
otubarplot(dstr97.f.p, main="97% OTUs")
otubarplot(dstr97bsp.f.p, main="97% within-species OTUs")
otubarplot(dstr97bs.f.p, main="97% within-sample OTUs")
otubarplot(dstr100.f.p, main="100% OTUs")
```
